Clause size reduction with all-UIP Learning

### 2020-02-21 paper.tex
added abstract

\documentclass[runningheads]{llncs}
\usepackage{times}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
%\usepackage[ruled,linesnumbered,noend,oldcommands]{algorithm2e}
\usepackage{xspace}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{array}
\usepackage{xcolor}
\usepackage{theorem}
\usepackage[T1]{fontenc}
% \usepackage[T1,hyphens]{url}
\usepackage{hyperref}
%\PassOptionsToPackage{hypnens}{url}
\title{Clause size reduction with all-UIP Learning}
\author{Nick Feng \and Fahiem Bacchus}
\authorrunning{N. Feng and F. Bacchus}
\institute{Department of Computer Science, University of Toronto, Canada, 
  \email{\{nfeng,fbacchus\}@cs.toronto.edu}}

@@

\begin{document}
\maketitle              % typeset the header of the contribution
% 
\begin{abstract}
\end{abstract}

>>>>

\documentclass[runningheads]{llncs}
\usepackage{times}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
%\usepackage[ruled,linesnumbered,noend,oldcommands]{algorithm2e}
\usepackage{xspace}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{array}
\usepackage{xcolor}
\usepackage{theorem}
\usepackage[T1]{fontenc}
% \usepackage[T1,hyphens]{url}
\usepackage{hyperref}
%\PassOptionsToPackage{hypnens}{url}

@@

\title{Clause size reduction with all-UIP Learning}
\author{Nick Feng \and Fahiem Bacchus}
\authorrunning{N. Feng and F. Bacchus}
\institute{Department of Computer Science, University of Toronto, Canada, 
  \email{\{nfeng,fbacchus\}@cs.toronto.edu}}

\begin{document}
\maketitle              % typeset the header of the contribution
% 
\begin{abstract}
    Almost all CDCL \sat solvers use the 1-UIP clause learning scheme
    to learn new clauses from conflicts, and our current understanding
    of \sat solving provides good reasons for using that scheme. In
    particular, the 1-UIP scheme yields asserting clauses, and these
    asserting clauses have minimum LBD among all possible asserting
    clauses. As a result of these advantages other clause learning
    schemes, like $i$-UIP and all-UIP, that had been proposed in early
    work are not used in modern solvers. In this paper, we propose a
    new technique for exploiting the all-UIP scheme in clause
    learning. Our technique is to employ all-UIP learning under the
    constraint that the clause's LBD does not increase (over the
    minimum established by the 1-UIP clause). Our method can generate
    clauses that are significantly smaller that the 1-UIP clause while
    not increasing the LBD. Unlike previous clause minimization
    methods, our technique is not limited to learning a sub-clause of
    the 1-UIP clause. It can instead learn a completely different
    clause. We show empirically that our method can improve the
    performance of state of the art solvers.
\end{abstract}
